\clearpage
\begin{thebibliography}{99}

\bibitem{RFC3986}
Berners-Lee T., Fielding R., Masinter L. 
Uniform Resource Identifier (URI): Generic Syntax.
Request for Comments: 3986, 2005

\bibitem{OIDC}
Sakimura~N., Bradley~J., Jones~M., de Medeiros~B., Mortimore~C. 
OpenID Connect Core 1.0 incorporating errata set 1.
Avail. at \url{http://openid.net/specs/openid-connect-core-1_0.html}, 2014

\bibitem{RFC6749}
Hardt~D., ed.
The OAuth 2.0 Authorization Framework.
Request for Comments: 6749, 2012

\bibitem{RFC6750}
Jones M., Hardt D.
The OAuth 2.0 Authorization Framework: Bearer Token Usage.
Request for Comments: 6750, 2012

\bibitem{ISO29115}
ISO/IEC 29115:2013, Information technology~---
Security techniques~--– Entity authentication assurance framework\\
{\small (Информационные технологии. Технологии безопасности. Инфраструктура 
аутентификации)}

\bibitem{SP800-63-3}
Grassi~P., Garcia~M., Fenton J.
NIST Special Publication 800-63-3. Digital Identity Guidelines.
U.S. Department of Commerce, National Institute of Standards and Technologies, 
2017

\bibitem{SP800-63-3A}
Grassi~P., Garcia~M., 
Lefkovitz~N., Danker~J., 
Choong~Y., Greene~K., Theofanos~M. 
NIST Special Publication 800-63-3A. Digital Identity Guidelines. Enrollment and 
Identity Proofing.
U.S. Department of Commerce, National Institute of Standards and Technologies, 
2017

\bibitem{SP800-63-3B}
Grassi~P., Fenton~J., Newton~E., Perlner~R., Regenscheid~A., Burr~W., Richer~J., 
Lefkovitz~N., Danker~J., 
Choong~Y., Greene~K., Theofanos~M. 
NIST Special Publication 800-63-3B. Digital Identity Guidelines. 
Authentication and Lifecycle Management.
U.S. Department of Commerce, National Institute of Standards and Technologies, 
2017

\bibitem{SP800-63-3C}
Grassi~P., Richer~J., Squire~S., Fenton~J., Nadeau~E., 
Lefkovitz~N., Danker~J., 
Choong~Y., Greene~K., Theofanos~M.
NIST Special Publication 800-63-3C. Digital Identity Guidelines. 
Federation and Assertion.
U.S. Department of Commerce, National Institute of Standards and Technologies, 
2017 

\bibitem{HTML4}
HTML 4.01 Specification. 
W3C Recommendation 24 December 1999.
Avail. at \url{https://www.w3.org/TR/1999/REC-html401-19991224/}, 1991

\bibitem{RFC4627}
Crockford D.
The application/json Media Type for JavaScript Object Notation (JSON).
Request for Comments: 4627, 2006

\bibitem{RFC7519}
Jones~M., Bradley~J., Sakimura~N. 
JSON Web Token (JWT).
Request for Comments: 7519, 2015

\bibitem{RFC5234}
Crocker D., ed.
Augmented BNF for Syntax Specifications: ABNF.
Request for Comments: 5234, 2008

\bibitem{RFC5646}
Phillips A., Davis M. 
Tags for Identifying Languages.
Request for Comments: 5646, 2009

\bibitem{RFC4648}
Josefsson S. 
The Base16, Base32, and Base64 Data Encodings.
Request for Comments: 4648, 2006

\bibitem{RFC5322}
Resnick P., ed. 
Internet Message Format.
Request for Comments: 5322, 2008

\bibitem{RFC6557}
Lear E., Eggert P.
Procedures for Maintaining the Time Zone Database.
Request for Comments: 6557, 2012

\bibitem{ISO639-1}
ISO 639-1:2002, Codes for the representation of names of languages~---
Part 1: Alpha-2 code\\
{\small (Коды для представления названий языков. Часть 1. Двухбуквенный код)}

\bibitem{ISO3166-1}
ISO 3166-1:1997, Codes for the representation of names of
countries and their subdivisions~--- Part 1: Country codes\\
{\small (Коды для представления названий стран и их подразделений. Часть 1. 
Коды стран)}

\bibitem{E-164}
E.164: The international public telecommunication numbering plan.
International Telecommunication Union, 2010

\bibitem{RFC3966}
Schulzrinne H. 
The tel URI for Telephone Numbers.
Request for Comments: 3966, 2004

\bibitem{RFC7515}
Jones~M., Bradley~J., Sakimura~N. 
JSON Web Signature (JWS).
Request for Comments: 7515, 2015

\bibitem{RFC7516}
Jones~M., Hildebrand~J. 
JSON Web Encryption (JWE).
Request for Comments: 7516, 2015

\bibitem{UTF8}
ISO/IEC 10646:2012, Information technology~--- Universal Coded Character Set 
(UCS)\\
{\small (Информационные технологии. Универсальный набор кодированных 
символов (UCS))}


\end{thebibliography}
